---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "README-"
)
```

# presidential_election_county_results_2016
presidential_election_county_results_2016

tidy election results updated 11/13/2016

the two files are identical. different names provided for continuity.

***UPDATED JAN 3, 2018***

## Data

Find the most up-to-date version of the data as a CSV or RDS (R data file) in the data directory.

### Long format

[Long format as .csv](data/pres.elect16.results.2018.csv): ./data/pres.elect16.results.2018.csv

```{r}
## long format CSV
readr::read_csv("data/pres.elect16.results.2018.csv")
```

[Long format as .rds](data/pres.elect16.results.2018.rds): ./data/pres.elect16.results.2018.rds

```{r}
## wide vote share data RDS
readr::read_rds("data/pres.elect16.results.2018.rds")
```


## Wide format - vote share

[Wide format vote share in
.csv](data/pres.elect16.results.wide.pct.2018.csv): ./data/pres.elect16.results.wide.pct.2018.csv

```{r}
## wide vote share data CSV
readr::read_csv("data/pres.elect16.results.wide.pct.2018.csv")
```

[Wide format vote share in
.rds](data/pres.elect16.results.wide.pct.2018.rds): ./data/pres.elect16.results.wide.pct.2018.rds

```{r}
## wide vote share data RDS
readr::read_rds("data/pres.elect16.results.wide.pct.2018.rds")
```

## Wide Format - total votes

[Wide format total votes in
.csv](data/pres.elect16.results.wide.votes.2018.csv): ./data/pres.elect16.results.wide.pct.2018.csv

```{r}
## wide vote totals data CSV
readr::read_csv("data/pres.elect16.results.wide.votes.2018.csv")
```

[Wide format total votes in
.rds](data/pres.elect16.results.wide.votes.2018.rds): ./data/pres.elect16.results.wide.pct.2018.rds

```{r}
## wide vote share data RDS
readr::read_rds("data/pres.elect16.results.wide.votes.2018.rds")
```
